Component response rate variation underlies the stability of complex systems (revision notes)

### 2020-01-13 notebook/revision_notes.Rmd
Work through notes

The curvature of the relationship between $\rho$ and $\max(\Re(\lambda))$ is consistent across different values of $S$, as shown below.

>>>>

The curvature of the relationship between $\rho$ and $\max(\Re(\lambda))$ is consistent across different values of $S$, as shown below. Including $\gamma$ always results in a concave upward relationship between $\rho$ and $\max(\Re(\lambda))$.

<!---

```{r, echo = FALSE}
sim10 <- read.csv(file = "sim_results/rhos/sim10.csv");
sim15 <- read.csv(file = "sim_results/rhos/sim15.csv");
sim20 <- read.csv(file = "sim_results/rhos/sim20.csv");
sim30 <- read.csv(file = "sim_results/rhos/sim30.csv");
sim35 <- read.csv(file = "sim_results/rhos/sim35.csv");
par(mar = c(1, 1, 1, 1), mfrow = c(3, 2), oma = c(5, 5, 1, 1));
plot(x = sim10[,1], y = sim10[,20], type = "b", pch = 20, lwd = 2, xaxt = "n");
points(x = sim10[,15], y = sim10[,21], type = "b", lwd = 2);
abline(h = 0, col = "red");
plot(x = sim15[,1], y = sim15[,20], type = "b", pch = 20, lwd = 2, xaxt = "n");
points(x = sim15[,15], y = sim15[,21], type = "b", lwd = 2);
abline(h = 0, col = "red");
plot(x = sim20[,1], y = sim20[,20], type = "b", pch = 20, lwd = 2, xaxt = "n");
points(x = sim20[,15], y = sim20[,21], type = "b", lwd = 2);
abline(h = 0, col = "red");
plot(x = sim25[,1], y = sim25[,20], type = "b", pch = 20, lwd = 2, xaxt = "n");
points(x = sim25[,15], y = sim25[,21], type = "b", lwd = 2);
abline(h = 0, col = "red");
plot(x = sim30[,1], y = sim30[,20], type = "b", pch = 20, lwd = 2);
points(x = sim30[,15], y = sim30[,21], type = "b", lwd = 2);
abline(h = 0, col = "red");
plot(x = sim35[,1], y = sim35[,20], type = "b", pch = 20, lwd = 2);
points(x = sim35[,15], y = sim35[,21], type = "b", lwd = 2);
abline(h = 0, col = "red");
mtext(text = "E correlation between A_ij and A_ji", side = 1,
      line = 0, outer = TRUE, cex = 1.5);
mtext(text = "E leading real part eigenvalue", side = 2,
      line = 1, outer = TRUE, cex = 1.5);
```

--->

### 2020-01-13 notebook/revision_notes.tex
Work through notes

\section{Role of correlated matrices in
stabilisation}\label{role-of-correlated-matrices-in-stabilisation}

@@

When \(\textbf{A}\) was stabilised by \(Var(\gamma)\), the change in
\(\rho\) was normally distributed around 0.001414 (95\% CIs: -0.0010192,
0.0040992). Hence, decreasing the correlation between
\(\textbf{A}_{ij}\) and \(\textbf{A}_{ji}\) was not by itself the cause
of stability. For a clearer picture of the effect of \(\gamma\), it is
useful to show the relationship between \(\rho\) and
\(\max(\Re(\lambda))\) again as above with, but this time with how the
relationship changes given \(Var(\gamma)\).

@@

In this red shaded region above, \(\max(\Re(\lambda))\) is decreased by
\(Var(\gamma)\). The shaded region encompasses values of \(\rho\)
between -0.4 and 0.8. But 1000 simulated \(\textbf{A}\) had values that
ranged between -0.240986 and 0.0704592, meaning that
\(\max(\Re(\lambda))\) was always expected to decrease given
\(Var(\gamma)\) even if \(Var(\gamma)\) caused \(\rho\) to increase.

>>>>

\hypertarget{role-of-correlated-matrices-in-stabilisation}{%
\section{Role of correlated matrices in
stabilisation}\label{role-of-correlated-matrices-in-stabilisation}}

@@

When \(\textbf{A}\) was stabilised by \(Var(\gamma)\), the change in
\(\rho\) was normally distributed around 0.001414 (95\% CIs: -0.0011599,
0.0040885). Hence, decreasing the correlation between
\(\textbf{A}_{ij}\) and \(\textbf{A}_{ji}\) was not by itself the cause
of stability. For a clearer picture of the effect of \(\gamma\), it is
useful to show the relationship between \(\rho\) and
\(\max(\Re(\lambda))\) again as above with, but this time with how the
relationship changes given \(Var(\gamma)\).

@@

In this red shaded region above, \(\max(\Re(\lambda))\) is decreased by
\(Var(\gamma)\). The shaded region encompasses values of \(\rho\)
between -0.4 and 0.7. But 1000 simulated \(\textbf{A}\) had values that
ranged between -0.240986 and 0.0704592, meaning that
\(\max(\Re(\lambda))\) was always expected to decrease given
\(Var(\gamma)\) even if \(Var(\gamma)\) caused \(\rho\) to increase.

The curvature of the relationship between \(\rho\) and
\(\max(\Re(\lambda))\) is consistent across different values of \(S\),
as shown below. Including \(\gamma\) always results in a concave upward
relationship between \(\rho\) and \(\max(\Re(\lambda))\).
